Unsupervised embedding of trajectories captures the latent structure of mobility

### 2020-12-03 paper/current/main.tex
implement Sada's corrections

\subsection*{Korean accommodation reservation data}
We source Korean accommodation reservation data from collaboration with Goodchoice Company LTD.. 
The data contains customer-level reservation trajectories spanning the period of August 2018 through July 2020 and comprising 1,038 unique accommodation locations in Seoul, South Korea.

@@

\begin{equation}
	\label{eq:linear_flux_geo}
	\ln\frac{T_{ij}}{m_im_j} = \ln C  - \alpha \ln g_{ij},S
\end{equation}

@@

%
% SUBSECTION: SEMAXIS
%
\subsection*{SemAxis}
SemAxis and similar studies~\autocite{an2018semaxis, nakandala2017gendered, kozlowski2018geometry} demonstrated that ``semantic axes'' can be found SemAxis and similar studies~\autocite{an2018semaxis, nakandala2017gendered, kozlowski2018geometry} demonstrated that ``semantic axes'' can be found from an embedding space by defining the ``poles'' and the latent semantic relationship along the semantic axis can be extracted with simple arithmetic.
In the case of natural language, the poles of the axis could be ``good'' and ``bad'', ``surprising'' and ``unsurprising'', or ``masculine'' and ``feminine''.
We can use SemAxis to leverage the semantic properties of the embedding vectors to operationalize abstract relationships between organizations.

>>>>

\subsection*{Korean accommodation reservation data}
We source Korean accommodation reservation data from collaboration with Goodchoice Company LTD.
The data contains customer-level reservation trajectories spanning the period of August 2018 through July 2020 and comprising 1,038 unique accommodation locations in Seoul, South Korea.

@@

\begin{equation}
	\label{eq:linear_flux_geo}
	\ln\frac{T_{ij}}{m_im_j} = \ln C  - \alpha \ln g_{ij},
\end{equation}

@@

%
% SUBSECTION: SEMAXIS
%
\subsection*{SemAxis}
SemAxis and similar studies~\autocite{an2018semaxis, nakandala2017gendered, kozlowski2018geometry} demonstrated that ``semantic axes'' can be found from an embedding space by defining the ``poles'' and the latent semantic relationship along the semantic axis can be extracted with simple arithmetic.
In the case of natural language, the poles of the axis could be ``good'' and ``bad'', ``surprising'' and ``unsurprising'', or ``masculine'' and ``feminine''.
We can use SemAxis to leverage the semantic properties of the embedding vectors to operationalize abstract relationships between organizations.
